ms_figures

### 2023-05-15 ms_figures.Rmd
clean up code for submission

fig3c <- ggplot() +
  geom_ribbon(data = fig3c_data %>%
                filter(supply_source == "domestic"),
              aes(ymin = supply_min_percent, ymax = supply_max_percent, x = year), fill = "grey70") +
  geom_ribbon(data = fig3c_data %>%
                filter(supply_source == "foreign"),
              aes(ymin = supply_min_percent, ymax = supply_max_percent, x = year), fill = "grey70") +
  geom_line(data = fig3c_data, aes(x = year, y = supply_percent, color = supply_source)) +
  scale_color_manual(values = c("#F37542", "#0F2D59")) +
  labs(x = "", y = "Percent of supply", color = "Origin") +
  lims(y = c(0,100)) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

ldc_net_habitat_method_summary <- ldc_net_habitat_method_summary %>%
  bind_rows(ldc_net_total)

@@

```{r, eval=FALSE}
# Plots moved from end of prep_data
top_processing_countries %>%
  filter(year == 2019) %>%
  ggplot(aes(x = live_weight_t, y = reorder(exporter_iso3c, ranking))) +
  geom_bar(stat = "identity") +
  scale_y_reordered() +
  theme_bw() +
  labs(x = "Re-exports (Live weight tonnes)", y = "Processing Country")

top_processing_countries_by_source %>%
  filter(year == 2019) %>%
  ggplot(aes(x = live_weight_t / 1000000, y = reorder(exporter_iso3c, ranking), fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  theme_bw() +
  labs(x = "Re-exports (Live weight million tonnes)", y = "Processing Country") +
  facet_wrap(~habitat_method, scales = "free_y")

>>>>

fig3c <- ggplot() +
  # geom_ribbon(data = fig3c_data %>%
  #               filter(supply_source == "domestic"),
  #             aes(ymin = supply_min_percent, ymax = supply_max_percent, x = year), fill = "grey70") +
  # geom_ribbon(data = fig3c_data %>%
  #               filter(supply_source == "foreign"),
  #             aes(ymin = supply_min_percent, ymax = supply_max_percent, x = year), fill = "grey70") +
  geom_line(data = fig3c_data, aes(x = year, y = supply_percent, color = supply_source)) +
  scale_color_manual(values = c("#F37542", "#0F2D59")) +
  labs(x = "", y = "Percent of supply", color = "Origin") +
  lims(y = c(0,100)) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

ldc_net_habitat_method_summary <- ldc_net_habitat_method_summary %>%
  bind_rows(ldc_net_total) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "total")))

@@
